Performing Cluster Analysis on TAD boundaries & Annotations

### 2019-03-15 Scripts/evaluating_pca.Rmd
saved heatmaps

```{r}

>>>>

```{r}
fileslst <- c(paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"), "/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_count.rds",sep=""),
              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_perc.rds",sep=""),
              paste("Z:/TAD_data_analysis/GM12878/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_GM12878_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_dist.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_K562_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_count.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_K562_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_perc.rds",sep=""),
              paste("Z:/TAD_data_analysis/K562/",c("10kb", "25kb", "50kb", "100kb"),"/Ensemble/PCA/pcadat_K562_", 
                    c("10kb", "25kb", "50kb", "100kb"), 
                    "_dist.rds",sep=""))

#file names for heatmaps
heatnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_heatmap.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_heatmap.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_heatmap.png", sep=""))

#file names for pca plots
scorepnames <- c(paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
               paste("gm12878", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_count", "_scoreplots.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_perc", "_scoreplots.png", sep=""),
               paste("k562", c("_10kb", "_25kb", "_50kb", "_100kb"), "_dist", "_scoreplots.png", sep=""))

for(i in 1:length(fileslst)){
  print(i)
  pcadata <- readRDS(fileslst[i])

  #performing log2 transformation only for distance predictor types
  if(grepl("_dist", colnames(pcadata)[1])){
    pcadata <- apply(pcadata,2,function(x){log(x + 1, base=2)})
  }

  #filtering low variance predictors
  nzv <- nearZeroVar(pcadata, saveMetrics= TRUE)
  nzvar <- rownames(nzv[nzv$nzv,])
  if(length(nzvar) > 0){ 
    pcadata_f <- pcadata[, -which(colnames(pcadata) %in% nzvar)]
    }else{pcadata_f <- pcadata}

  #cleaning column names
  colnames(pcadata_f) <- gsub(paste(c("`", 
                                                    "_",
                                                    "-",
                                                    "Gm12878",
                                                    "K562", 
                                                    "dist",
                                                    "count",
                                                    "perc",
                                                    "Haib", 
                                                    "Sydh",
                                                    "Uta",
                                                    "Uw",
                                                    "Broad",
                                                    "Uchicago"), collapse = "|"),"", colnames(pcadata_f))

  #heatmap 
  my_palette <- rev(colorRampPalette(brewer.pal(11, "RdBu"))(100))
  png(filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", heatnames[i], sep=""),
      width=11, height=8, units="in", res = 300)
  heatmap.2(pcadata_f,
          #cellnote = ,  # same data set for cell labels
          #main = "", # heat map title
          notecol="black",      # change font color of cell labels to black
          density.info="none",  # turns off density plot inside color legend
          trace="none",         # turns off trace lines inside the heat map
          #margins =c(5,5),     # widens margins around plot
          col=my_palette,       # use on color palette defined earlier
          #na.color = "gray",
          #breaks=col_breaks,    # enable color transition at specified limits
          key=TRUE,
          dendrogram="column",     # only draw a row dendrogram
          cexRow=0.5,
          cexCol=0.5,
          labRow = FALSE,
          #lmat=rbind( c(0, 3), c(2,1), c(0,4) ), 
          #lhei=c(.5,6,0),
          #sepwidth=c(0.001,0.001),
          #sepcolor="black",
          #colsep=1:ncol(pcadata_f),
          #rowsep=1:nrow(pcadata_f),
          keysize = 1) 
  dev.off()

  #PCA
  #pcadata_f <- t(pcadata_f)
  #Group <- ifelse(rownames(pcadata_f) %in% cs, "Chromatin State", ###chromatin states
  #                                          ifelse(rownames(pcadata_f)=="DNase", "DNase I", ###dnase
  #                                                 ifelse(rownames(pcadata_f) %in% hm, "Histone Modification", ###histone modifications
  #                                                        "TFBS"))) ###transcription factor binding sites
  #pcadata_f <- cbind.data.frame(pcadata_f, Group)
  #
  ###Plots without loadings
  #p <- autoplot(prcomp(pcadata_f[,-(dim(pcadata_f)[2])]),
  #       #loadings = TRUE,
  #       label = TRUE, 
  #       label.size = 3,
  #       label.repel=T,
  #       data=pcadata_f,
  #       colour='Group',
  #       label.show.legend = FALSE) +
  #theme_bw()

  #ggsave(p, filename = paste("C:/Users/stili/Documents/TAD_miscellaneous/figures/pca_plots/", 
  #                           scorepnames[i], sep=""),
  #       width=8, height=11, units="in", dpi=300)

}
